Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-12-06 bayesian-analysis/kundinger-ba-2021.tex
working on compiling ba paper.

% \documentclass[ba,preprint]{imsart}% use this for supplement article
\documentclass[ba]{imsart}
%
\pubyear{2021}
\volume{TBA}
\issue{TBA}
% \doi{0000}
%\arxiv{}
\firstpage{1}
\lastpage{1}

@@

\startlocaldefs
% ** Local definitions **
\endlocaldefs

@@

@@

\begin{frontmatter}
\title{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}
%\title{A Sample Document\thanksref{T1}}
%\thankstext{T1}{<thanks text>}
\runtitle{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}

@@

%\address[addr2]{Departments of Statistical Science and Computer Science,
%  Duke University,
%  P.O.\ Box 90251,
%  Durham, NC 27708, USA
%  \printead{e3}
%}

@@

%% ** Keywords **
\begin{keyword}%[class=MSC]
bipartite record linkage, Bayesian methods, Gibbs sampling, hashing techniques, Markov chain Monte carlo, parallel/distributed computing
%\kwd{}
%\kwd[]{}
\end{keyword}

>>>>

\documentclass[ba,preprint]{imsart}% use this for supplement article
%\documentclass[ba]{imsart}
%%
%\pubyear{2021}
%\volume{TBA}
%\issue{TBA}
%% \doi{0000}
%%\arxiv{}
%\firstpage{1}
%\lastpage{1}
%\input{subfiles/preamble.tex}

@@

%\startlocaldefs
%% ** Local definitions **
%\endlocaldefs

@@

\begin{frontmatter}

@@

\begin{frontmatter}
\title{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}
%\title{A Sample Document\thanksref{T1}}
%\thankstext{T1}{<thanks text>}
\runtitle{Efficient and Scalable Bipartite Matching with Fast Beta Linkage  (fabl)}
%
%\begin{aug}
%\author{\fnms{Neil G.} \snm{Marchant}\thanksref{addr1}\ead[label=e1]{nmarchant@unimelb.edu.au}},
%\author{\fnms{Benjamin I. P.} \snm{Rubinstein}\thanksref{addr1}\ead[label=e2]{brubinstein@unimelb.edu.au}}
%\and
%\author{\fnms{Rebecca C.} \snm{Steorts}\thanksref{addr2}\ead[label=e3]{beka@stat.duke.edu}}
%
%\runauthor{N. G. Marchant et al.}
%
%\address[addr1]{School of Computing and Information Systems,
%  University of Melbourne,
%  Parkville, VIC 3010, Australia,
%  \printead{e1}, % print email address of "e1"
%  \printead*{e2}
%}
%
%\address[addr2]{Departments of Statistical Science and Computer Science,
%  Duke University,
%  P.O.\ Box 90251,
%  Durham, NC 27708, USA
%  \printead{e3}
%}
%
%%\thankstext{<id>}{<text>}
%
%\end{aug}

@@

\address[addr2]{Departments of Statistical Science and Computer Science,
  Duke University,
  P.O.\ Box 90251,
  Durham, NC 27708, USA
  \printead{e3}
}

@@

%% ** Keywords **
\begin{keyword}%[class=MSC]
\kwd{entity resolution}
\kwd{record linkage}
\kwd{deduplication}
\kwd{Bayesian methods}
\kwd{Markov chain Monte Carlo}
%\kwd[]{}
\end{keyword}

%%% ** Keywords **
%\begin{keyword}%[class=MSC]
%bipartite record linkage, Bayesian methods, Gibbs sampling, hashing techniques, Markov chain Monte carlo, parallel/distributed computing
%%\kwd{}
%%\kwd[]{}
%\end{keyword}
